PCA

### 2020-01-23 analysis/02_PCA.Rmd
pca with new colors

abc2 <- plot_grid(a2,b2,c2, nrow = 1, labels = c("a", "b", "c"), label_size = 12)
abc2

@@

def2 <- plot_grid(d2,e2, f2, nrow =  1,  labels = c("d", "e", "f"), label_size = 12)
def2
```

@@

gh2 <- plot_grid(g2,h2, legend2, nrow = 1, rel_widths = c(1, 1, 1), labels = c("h", "i", NULL ), label_size = 12)
gh2
plot_grid(def2, gh2, nrow = 2)
```

```{r PCA-tSNE, fig.height= 7, fig.width=7}
plot_grid( abc, def, gh, nrow = 3)
plot_grid( abc2, def2, gh2, nrow = 3)

@@

>>>>

abc2 <- plot_grid(a2,b2,c2, nrow = 1, labels = c("a", "b", "c"), label_size = 12)
abc2
```

@@

def2 <- plot_grid(d2,e2, f2, nrow =  1,  labels = c("d", "e", "f"), label_size = 12)
def2

@@

gh2 <- plot_grid(g2,h2, legend2, nrow = 1, rel_widths = c(1, 1, 1), labels = c("h", "i", NULL ), label_size = 12)
gh2
plot_grid(def2, gh2, nrow = 2)

@@

```{r PCA-tSNE, fig.height= 7, fig.width=7}
plot_grid( abc, def, gh, nrow = 3)
plot_grid( abc2, def2, gh2, nrow = 3)
```
